Forecasting the 2024 U.S. Presidential Election: Polling Trends and Dynamics Based on National General Election Polls

### 2024-11-05 paper/paper.qmd
test

This study employs various R packages (@R) for data cleaning and analysis, including libraries from tidyverse (@tidyverse), ggplot2 (@ggplot2), rstanarm (@rstanarm), testthat (@Test), here (@Here), janitor (@janitor), lubridate (@lubridate), broom (@broom), dplyr (@dplyr), knitr (@knitr), and modelsummary (@ModelSummary). Lastly, the arrow was used to store data efficiently.

@@

# Find the missing states by comparing with the list of all states
missing_states <- setdiff(all_states, states_in_winners)

# Create a data frame for the missing states with "Uncertainty" as the candidate
missing_states_df <- data.frame(
  state = missing_states,
  candidate_name = "Uncertainty",
  avg_support = NA,  # Since we don't have support data for missing states
  sd_support = NA,
  electoral_votes = NA,
  abbr = state.abb[match(missing_states, state.name)] # Add state abbreviations
)

# Add the missing states to the winners dataset
winners <- bind_rows(winners, missing_states_df)

>>>>

This study employs various R packages (@R) for data cleaning and analysis, including libraries from tidyverse (@tidyverse), ggplot2 (@ggplot2), rstanarm (@rstanarm), testthat (@Test), here (@Here), janitor (@janitor), lubridate (@lubridate), broom (@broom), dplyr (@dplyr), knitr (@knitr), and modelsummary (@ModelSummary). Lastly, arrow (@arrow) was used to store data efficiently.

@@

# Find the missing states
missing_states <- setdiff(all_states, states_in_winners)

# Proceed only if there are missing states
if (length(missing_states) > 0) {
  # Create a data frame for the missing states with "Uncertainty" as the candidate
  missing_states_df <- data.frame(
    state = missing_states,
    candidate_name = rep("Uncertainty", length(missing_states)),
    avg_support = rep(NA, length(missing_states)),  # Since we don't have support data for missing states
    sd_support = rep(NA, length(missing_states)),
    electoral_votes = rep(NA, length(missing_states)),
    abbr = state.abb[match(missing_states, state.name)]  # Add state abbreviations
  )

  # Add the missing states to the winners dataset
  winners <- bind_rows(winners, missing_states_df)
} else {
  message("No missing states found.")
}
